Generate data for NOBA cod ensemble modeling

### 2021-05-06 NOBAcod.Rmd
add noba files and script

#Load in model object from SAM
noba_cod_out <- system.file("inst","extdata","NOBA_cod_files","NEAcod-2020","run","model.RData",
                            package = "atlantisom") 
#This is the SAM object
noba_fit <- noba_cod_out$fit

properties <- c("minAge","maxAge", "maxAgePlusGroup")

age_info <- lapply(properties, get, noba_fit$conf)
names(age_info) <- properties

#install SAM
remotes::install_github("fishfollower/SAM/stockassessment")
require(stockassessment)

#Month of survey/fishing
#survey_month <- 7
#fishing_month <- 1

>>>>

#Load in model object from SAM
noba_cod_out <- system.file("inst","extdata","NOBA_cod_files","NEAcod-2020","run","model.RData",
                            package = "atlantisom") 
#Month of survey/fishing
#survey_month <- 7
#fishing_month <- 1
